---
title: "Data extraction report"
author: "Your name"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  project: 'project name'
  plot_type: 
      value: 'plotly'
      choices: ['highcharter', 'ggplot2', 'plotly']
  month_start: '2020-01-01'
  month_end: '2021-09-01'
---

<!-- (using parameters in Rmarkdown; don't forget the r) -->
<!-- (This statement above all tabs) -->
This is my report data extraction report for `r paste(params$project)`. I'm creating a plot using `r paste(params$plot_type)`.  

<!-- (making tabs) -->
<!-- # header 1, all tabs need to be ## header 2 to nest -->

# {.tabset .tabset-pills}

## Some Info {.tabset .tabset-pills}

Click bottons below to find details about this data extraction.

### Set up

<!-- (here is an R code chunk; I've used some options to hide things) -->


```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = TRUE,
                      message = TRUE)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(ggthemes)
library(MNColorrrs)
library(odbc)
library(flextable)
library(broom)
library(oddsratio)
library(patchwork)
library(rstatix)
library(eaesdrrr)
library(DT)
library(reactable)
library(plotly)
library(highcharter)
library(skimr)
library(DataExplorer)
library(janitor)
library(DBI)
create_folders()
```

### Data warehouse access

```{r data warehouse, include=FALSE}
dw_uid <- rstudioapi::showPrompt( #PW for connecting to the DW
  title = "What is your PW?",
  message = "What is your PW?",
  default = "")

con <- dbConnect(odbc::odbc(),
                 "Terapass",
                 timeout = Inf,
                 UID = keyring::key_list("data-warehouse")[1,2],
                 PWD = keyring::key_get("data-warehouse", dw_uid),
                 big.int = "numeric")

```

### Functions

describe the function here...

```{r}
q_elig_person <- function(in_connection,in_month,in_programid)
{
  in_connection %>% 
    tbl(
      sql(
        glue::glue(
          "
SELECT a.CaseNumber
, b.PersonIDcurrent
, date'{in_month}' as report_month
FROM MaxisViews.CAFSApprovalV a 
INNER JOIN MaxisViews.CAFSPersonTestResultsV b
ON a.CaseNumber = b.CaseNumber
AND a.ProgramID = b.ProgramID
AND a.TestBenefitMo = b.BenefitMonth
AND a.TestSequence = b.SequenceNumber
WHERE a.BenefitMonth >= Add_Months(DATE'{in_month}' , -25) 
AND a.BenefitMonth < Add_Months(DATE'{in_month}' , +1)
AND a.DerivedEndDate > DATE'{in_month}' 
AND a.ProgramStatCode = 'A'
AND a.ResultCode <> 'I'
AND a.ProgramID = '{in_programid}' 
--AND a.issueongoingamount >0 
 AND b.MembershipCode = 'A' 
 "
)
)
) %>% 
    collect()
}
 
```


### Months of extraction

Months of data extraction for this request.

```{r}
mnths <- seq.Date(from = ymd(params$month_start),
                  to = ymd(params$month_end),
                  by = "month")
mnths
```


### Data extraction

Iterating data extraction function over the period of months defined above.

```{r}
d <- mnths %>% 
  purrr::map_dfr(~q_elig_person(con,.,in_programid = 'FS'))
```


### Saving data

All extracted data saved together for use elsewhere. 

```{r}
save(d,
     file = here::here('data',
                       glue::glue("{str_replace_all(params$project,' ','-')}-{today()}.RData")))
```


<!-- I can directly add HTML into my document -->
<details>
<summary> Analysts might want to know this information </summary>
```{r}
tribble(~DateType,~Date,
        "Eligibilty month start", params$month_start,
        "Eligibilty month end", params$month_end) %>% 
  DT::datatable(filter = 'top', extensions = 'Buttons', 
              options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel')))
```
</details>

## Interactive Data Tables {.tabset .tabset-pills}
<!-- Try changing .tabset-pills to .tabset-dropdown -->

For large datasets, sampling only 2000 rows. 

### Results

```{r}
if (count(d) < 2000)
{
  DT::datatable(d, filter = 'top', extensions = 'Buttons', 
                options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel')))
} else
{
  DT::datatable(d |> sample_n(size = 2000), filter = 'top', extensions = 'Buttons', 
                options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel')))
}
```


## Data Exploration {.tabset .tabset-pills}
<!-- Try changing .tabset-pills to .tabset-dropdown -->

### Data structure

```{r}
d %>% plot_str()
```

### Summary statistics

```{r}
d |> skim()
```

### Check for duplicates

```{r}
d %>% get_dupes()
```

### Correlations

```{r}
d %>% plot_correlation()
```

## Interactive or Fixed Plot

<!-- (Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.) -->
```{r plot, fig.width=10}

myplot <- 
  d |> 
  group_by(report_month) |> 
  summarise_all(~n_distinct(.)) %>% 
  pivot_longer(cols = -report_month) |> 
  ggplot(aes(x = report_month, y = value, fill = name)) + 
  geom_line() +
  facet_wrap(Program~.,scales = 'free') +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_mn_state(palette = "accent") +
  theme_fivethirtyeight() +
    themer()

if(params$plot_type == 'plotly'){
  #Dynamic plot with plotly 
  ggplotly(myplot)
  
}else if (params$plot_type == 'highcharter'){
  
 #Dynamic plot with highcharter
 df %>% 
    dplyr::select(Date, Category, UR)  %>% 
    highcharter::hchart(., 
         type = "line", 
         hcaes(x = Date, 
               y = UR, 
               group = Category)) %>% 
  hc_yAxis(opposite = TRUE,
           labels = list(format = "{value}%")) %>% 
  hc_tooltip(pointFormat = '{point.x:%Y-%m-%d}')
  
}else if (params$plot_type == 'ggplot2'){
  #Fixed ggplot
  myplot
}

```
