---
title: "Programs Needs Report"
author: "Ben Jaques-Leslie and Taylor Vonderharr"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
params:
  in_file: "WECARE DataPull 1.xlsx"
  in_start_date: "2023-05-01"
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readtext)
library(DBI)
library(lubridate)
library(readxl)
library(arsenal)
library(janitor)
library(skimr)
library(ggthemes)
library(naniar)
library(writexl)
library(magrittr)
library(flextable)
library(openxlsx)
source("report_functions.R")
source("Summarize_WEN_Functions.R")
# load(here::here("data","question_list.Rdata"))
```




## Load and Prepare data 

## Assessment data

We will probably need to update this to work on Noorie's computer. 

```{r}
d <-
  # file.path(
  #   "/Users/noorie/Dropbox/My Mac (Noorjehans-MacBook-Pro.local)/Documents/WECARE R",
  #   "DATA",
  #   "Renamed Data",
  #   params$in_file
  # ) %>%
  here::here(
    "data",
    params$in_file
  ) %>% 
  clean_WECARE()

d %>% 
  glimpse()
```

## Assessment data

We will probably need to update this to work on Noorie's computer. 

```{r}
q <-
  # file.path(
  #   "/Users/noorie/Dropbox/My Mac (Noorjehans-MacBook-Pro.local)/Documents/WECARE R",
  #   "DATA",
  #   "Renamed Data",
  #   "wecare-referral-question-list.xlsx"
  # ) %>%
  here::here(
    "data",
    "wecare-referral-question-list.xlsx"
  ) %>% 
  read_xlsx()

q %>% 
  glimpse()
```
## tidy strings

```{r}
d <- 
  d %>% 
  mutate_if(is.character,~str_trim(.)) 

d %>% 
  glimpse()
```

## Remove test people
```{r}
d <- d %>% 
  filter(!str_detect(str_replace_all(person_name, regex("\\W+")," "),regex("test person",ignore_case = TRUE))
         )

d %>%
  select(person_name) %>% 
  distinct()
```
## Identifying Families 
```{r}
family_assessments <- 
  d %>% 
  filter(number_of_children>0) %>% 
  select(intake_id) %>% 
  distinct()
family_assessments
```


## tall questions

```{r}
tall_q <- 
  d %>% 
  select(intake_id,contains("_question_"),contains("assist_")) %>% 
  pivot_longer(-intake_id)

tall_q
```

## Join referral questions

```{r}
prep_01 <- 
  tall_q %>% 
  left_join(q)

prep_01 %>% 
  skim()
```
## Filter to only SDOH responses

```{r}
prep_02 <- 
  prep_01 %>% 
  filter(sdoh_questions == 1)

prep_02 %>% 
  skim()
```

## Align answer order for SDOH questions

```{r}
prep_03 <- 
  prep_02 %>% 
  mutate(
    value_aligned = case_when(answer_order == "default" ~ value,
                              answer_order == "reverse" & value == "Yes" ~ "No",
                              answer_order == "reverse" & value == "No" ~ "Yes",
                              answer_order == "reverse" ~ value
                              ),
    value_aligned = factor(value_aligned)
  )

prep_03 %>% 
  skim()
```


## WECARE Assessments Completed
```{r}
prep_01 <- d %>% 
  summarise(n=n_distinct(intake_id)) %>% 
  mutate(label="WECARE Assessments Completed") %>% 
  select(label,n)
prep_01
```

## Tribal programs made referrals
find number in WECARE teams folder

## WECARE Assessments with no response needed
```{r}
prep_02 <- tall_q %>% 
  group_by(intake_id,value,.drop=FALSE) %>% 
  count() %>% 
  ungroup() %>%
  filter(value=="Urgent Need") %>% 
  filter(n==0) %>% 
  summarise(n=n_distinct(intake_id)) %>% 
  mutate(label="WECARE Assessments with no response needed") %>% 
  select(label,n)
prep_02
```

## Families identified an Urgent Need
```{r}
prep_03 <- tall_q %>% 
  inner_join(family_assessments) %>% 
  group_by(intake_id,value,.drop=FALSE) %>% 
  count() %>% 
  ungroup() %>%
  filter(value=="Urgent Need") %>% 
  filter(n>0) %>% 
  summarise(n=n_distinct(intake_id)) %>% 
  mutate(label="Families identified an Urgent Need") %>% 
  select(label,n)
prep_03
```

## Individuals identified an Urgent Need
```{r}
prep_07 <- tall_q %>% 
  anti_join(family_assessments) %>% 
  group_by(intake_id,value,.drop=FALSE) %>% 
  count() %>% 
  ungroup() %>%
  filter(value=="Urgent Need") %>% 
  filter(n>0) %>% 
  summarise(n=n_distinct(intake_id)) %>% 
  mutate(label="Individuals identified an Urgent Need") %>% 
  select(label,n)
prep_07
```




## Referrals were made to tribal programs

```{r}
prep_04 <- 
  tall_q %>% 
  filter(value=="Urgent Need") %>% 
  count() %>% 
  mutate(label="Referrals were made to tribal programs") %>% 
  select(label,n)
prep_04
```


## Substance abuse related referrals were made

```{r}
prep_05 <- 
  tall_q %>% 
  filter(
    name == "emotional_substance_use_question_one_substance_use_is_effecting_my_family_and_i_need_help" |
      name == "emotional_substance_use_question_two_i_am_active_in_sobriety_and_would_be_willing_to_help_others" |
      name == "emotional_substance_use_question_three_i_would_like_more_information_about_addiction" |
      name == "emotional_substance_use_question_five_i_would_like_more_information_about_support_services" |
      name == "emotional_children_question_one_i_have_concerns_about_my_children_having_behavioral_broblems_at_school_home_or_in_the_community"| 
      name == "emotional_children_question_one_i_have_concerns_about_my_children_having_behavioral_broblems_at_school_home_or_in_the_community"|
      name == "emotional_client_question_one_i_have_experience_a_traumatic_event_in_my_life" |
      name == "emotional_client_question_two_do_you_feel_sad_or_unhappy_frequently" |
      name == "emotional_client_question_three_i_believe_me_or_my_children_would_benefit_from_mental_health_services"|
      name == "emotional_substance_use_question_one_substance_use_is_effecting_my_family_and_i_need_help" |
      name == "emotional_substance_use_question_two_i_am_active_in_sobriety_and_would_be_willing_to_help_others" |
      name == "emotional_substance_use_question_three_i_would_like_more_information_about_addiction" |
      name == "emotional_substance_use_question_five_i_would_like_more_information_about_support_services"
    ) %>% 
  filter(    
    value == "Urgent Need"
  ) %>%
  distinct() %>% 
  count() %>% 
  mutate(label="Substance Abuse referrals were made") %>% 
  select(label,n)
prep_05
```


## Warm handoffs made connecting families
Find numbers in rite track notes and program referral reminder email responses 

## Top 3 programs that received referrals

```{r}
# prep_06 <- 
# tall_q %>% 
#   left_join(question_list) %>% 
#   rename(referral_program=program) %>% 
#   mutate(
#   referral_program=as.factor(referral_program)) %>% 
#   filter(value=="Urgent Need"|
#            (referral_program=="Enrollments"& value=="Yes")|
#          (referral_program=="CHR"& value=="Yes")) %>% 
#   group_by(referral_program,.drop=FALSE) %>% 
#   summarize(n=n_distinct(intake_id)) %>% 
#   arrange(desc(n)) %>% 
#   mutate(label="Top 3 programs where referrals were made") %>% 
#   select(label,referral_program,n)
# prep_06
```

## Save to xlsx

### List of dataframes

```{r}
df_list <- mget(ls(pattern = "^prep_.*"))
```

### remove "prep_" from data frame names

```{r}
names(df_list) <- 
  names(df_list) %>% 
  str_remove("prep_")
```

### Define File Name

```{r}
excel_file_name <- 
paste0("monthly_wecare_update","_",str_replace_all(params$in_start_date,"-","_"),
                      "_created_",
                      str_replace_all(Sys.Date(),"-","_"),
                      ".xlsx")  
  
```



### Save
```{r}
output <- bind_rows(df_list)
```


```{r}
output %>% 
  write_xlsx(
    here::here("output",
               "excel",
               excel_file_name
               )
  )
```


### Reformat Excel
```{r}
wb <- 
  loadWorkbook(
    file=here::here("output",
               "excel",
               excel_file_name
               )
  )
```


```{r}
# setColWidths(wb,sheet=1,cols=1:length(output),
#              widths = 
#                c(43.71,
#                  8.43,
#                  38.14))
```

```{r}
style <- createStyle(halign = "center")
addStyle(wb,sheet = 1,cols = 2,rows = 2:(nrow(output)+1),style = style)
```


```{r}
saveWorkbook(wb,
             file=here::here("output",
               "excel",
               excel_file_name
               ),
             overwrite = TRUE)
```

