---
title: "Programs Needs Report"
author: "Ben Jaques-Leslie and Taylor Vonderharr"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
params:
  in_file: "WECARE DataPull 1.xlsx"
  in_start_date: "2023-05-01"
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readtext)
library(DBI)
library(lubridate)
library(readxl)
library(arsenal)
library(janitor)
library(skimr)
library(ggthemes)
library(naniar)
library(writexl)
library(magrittr)
library(flextable)
library(openxlsx)
source("report_functions.R")
source("Summarize_WEN_Functions.R")
# load(here::here("data","question_list.Rdata"))
```




## Load and Prepare data 

## Assessment data

We will probably need to update this to work on Noorie's computer. 

```{r}
d <-
  # file.path(
  #   "/Users/noorie/Dropbox/My Mac (Noorjehans-MacBook-Pro.local)/Documents/WECARE R",
  #   "DATA",
  #   "Renamed Data",
  #   params$in_file
  # ) %>%
  here::here(
    "data",
    params$in_file
  ) %>% 
  clean_WECARE()

d %>% 
  glimpse()
```

## Assessment data

We will probably need to update this to work on Noorie's computer. 

```{r}
q <-
  # file.path(
  #   "/Users/noorie/Dropbox/My Mac (Noorjehans-MacBook-Pro.local)/Documents/WECARE R",
  #   "DATA",
  #   "Renamed Data",
  #   "wecare-referral-question-list.xlsx"
  # ) %>%
  here::here(
    "data",
    "wecare-referral-question-list.xlsx"
  ) %>% 
  read_xlsx()

q %>% 
  glimpse()
```
## tidy strings

```{r}
d <- 
  d %>% 
  mutate_if(is.character,~str_trim(.)) 

d %>% 
  glimpse()
```

## Remove test people
```{r}
d <- d %>% 
  filter(!str_detect(str_replace_all(person_name, regex("\\W+")," "),regex("test person",ignore_case = TRUE))
         )

d %>%
  select(person_name) %>% 
  distinct()
```
## Identifying Families 
```{r}
family_assessments <- 
  d %>% 
  filter(number_of_children>0) %>% 
  select(intake_id) %>% 
  distinct()
family_assessments
```


## tall questions

```{r}
tall_q <- 
  d %>% 
  select(intake_id,contains("_question_"),contains("assist_")) %>% 
  pivot_longer(-intake_id)

tall_q
```

## Join referral questions

```{r}
prep_01 <- 
  tall_q %>% 
  left_join(q)

prep_01 %>% 
  skim()
```
## Filter to only SDOH responses

```{r}
prep_02 <- 
  prep_01 %>% 
  filter(sdoh_questions == 1)

prep_02 %>% 
  skim()
```

## Align answer order for SDOH questions

```{r}
prep_03 <- 
  prep_02 %>% 
  mutate(
    value_aligned = case_when(answer_order == "default" ~ value,
                              answer_order == "reverse" & value == "Yes" ~ "No",
                              answer_order == "reverse" & value == "No" ~ "Yes",
                              answer_order == "reverse" ~ value
                              ),
    value_aligned = factor(value_aligned)
  )

prep_03 %>% 
  skim()
```

## Count assessments by response

```{r}
tbl_1 <- 
  prep_03 %>% 
  group_by(value_aligned) %>% 
  summarise(n = n_distinct(intake_id)) %>% 
  arrange(desc(value_aligned)) %>% 
  ungroup()

tbl_1
```

## Count assessments by response and referred office

```{r}
tbl_2 <- 
  prep_03 %>% 
  group_by(value_aligned,program) %>% 
  summarise(n = n_distinct(intake_id)) %>% 
  arrange(desc(value_aligned),program) %>% 
  ungroup()

tbl_2
```

## Save excel

```{r}
write_xlsx(list("Overall" = tbl_1, "By referred program" = tbl_2),path = here::here("output","xlsx",
                                               glue::glue("wecare-sdoh-question-{params$in_start_date}.xlsx")
                                               )
)
```


